Results from the deep learning challenge associated with the 3MD4040 lecture on plankton classification

### 2022-05-06 Report/paper.tex
fix path, show sizes
fix paper fig/table paths

\begin{figure}
	\begin{center}
		% \includegraphics[width=0.3\columnwidth]{figs/size_train.png}
		% \includegraphics[width=0.3\columnwidth]{figs/sizes_test.pdf}
		% \includegraphics[width=0.3\columnwidth]{figs/size_orig.png}
	\end{center}
	\caption{\label{fig:sizes} Distribution of the image sizes for the training set (left), test set(right) and the original dataset (right). On the plot on the right, the original sizes have been limited to $4000$ for both widths and heights but there exists outliers up to $10000$ in width or $12000$ in height.}
\end{figure}

@@

\input{table_best_predicted.tex}

@@

\input{table_worst_predicted.tex}

@@

\begin{figure}
	\begin{tabular}{ccccc}
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_spongebob.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_cestquilepatron.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_deepwhale.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_granderegazzoni.png}&
	\includegraphics[width=0.18\columnwidth]{conffigs/usion_matrix_TheBackpropagatedStubborns.png}\\
		SpongeBob & C'est qui l'patron & DeepWhalfigs/e & GrandeRegazzoni & The Backpropagated Stubborns\\
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_MetzDreamDeep.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_voleursDhuile.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_JMBmc.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_AG0D.png}&
	\includegraphics[width=0.18\columnwidth]{conffigs/usion_matrix_ResMetz.png}\\
		Metz Dream Deep & Voleurs d'Huile & JMBmcfigs/ & AG0D\\
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_CelestineFeuillat.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_LesJongleurs.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_DeepBeru'4s.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_TheWhaleSharks.png}&\\
		CelestineFeuillat & LesJongleurs & DeepBeru'4s & TheWhaleSharks & 
	\end{tabular}
	\caption{\label{fig:confusion} Confusion matrices of the best submissions of all the participants.}
\end{figure}

@@

% python3 plot_stats.py /opt/Datasets/ZooScan/train /opt/Datasets/ZooScan/derived.csv
\input{stat_table.tex}

>>>>

\begin{figure}
	\begin{center}
		\includegraphics[width=0.3\columnwidth]{figs/size_train.png}
		\includegraphics[width=0.3\columnwidth]{figs/sizes_test.png}
		\includegraphics[width=0.3\columnwidth]{figs/size_orig.png}
	\end{center}
	\caption{\label{fig:sizes} Distribution of the image sizes for the training set (left), test set(right) and the original dataset (right). On the plot on the right, the original sizes have been limited to $4000$ for both widths and heights but there exists outliers up to $10000$ in width or $12000$ in height.}
\end{figure}

@@

\input{./figs/table_best_predicted.tex}

@@

\input{./figs/table_worst_predicted.tex}

@@

\begin{figure}
	\begin{tabular}{ccccc}
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_spongebob.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_cestquilepatron.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_deepwhale.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_granderegazzoni.png}&
        \includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_TheBackpropagatedStubborns.png}\\
		SpongeBob & C'est qui l'patron & DeepWhalfigs/e & GrandeRegazzoni & The Backpropagated Stubborns\\
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_MetzDreamDeep.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_voleursDhuile.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_JMBmc.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_AG0D.png}&
        \includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_ResMetz.png}\\
		Metz Dream Deep & Voleurs d'Huile & JMBmcfigs/ & AG0D\\
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_CelestineFeuillat.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_LesJongleurs.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_DeepBeru'4s.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_TheWhaleSharks.png}&\\
		CelestineFeuillat & LesJongleurs & DeepBeru'4s & TheWhaleSharks & 
	\end{tabular}
	\caption{\label{fig:confusion} Confusion matrices of the best submissions of all the participants.}
\end{figure}

@@

% python3 plot_stats.py /opt/Datasets/ZooScan/train /opt/Datasets/ZooScan/derived.csv
\input{./figs/stat_table.tex}
